---
title: "Dan Warren"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---


<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>

# About Me

I have broad interests across evolution, ecology, biogeography, and conservation biology.  My primary research program focuses on using informatics approaches to answer large-scale questions in population biology, with a particular focus on species distribution models/environmental niche models.  I also have active research programs in phylogenetic methods and theory, and neuroecology of marine fishes.  I tend to do a lot of quantitative and computational methods development, and have developed several widely-used software packages for population biologists.




# Publications (last updated `r Sys.Date()`)

For the most up-to-date information on what I've been doing, check [Google Scholar](http://scholar.google.com/citations?user=NTzu9c8AAAAJ&hl=en).  You can also check me out on [Orcid](http://orcid.org/0000-0002-8747-2451), [ResearcherID](http://www.researcherid.com/rid/B-3821-2010), or [Scopus](http://www.scopus.com/authid/detail.url?authorId=7202133982), but those are updated considerably less often.
<br>
<br>
The following is scraped automatically from Google Scholar, and may contain errors depending on API changes, formatting issues, or the direction of the wind.  For an up-to-date and correct CV, [email me](mailto:dan.l.warren@gmail.com).
<br>
<br>
<div class="col2">
```{r citeplot, echo = FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60), results="asis", fig.align="center"}
library(rcrossref)
library(pander)
library(scholar)
library(ggplot2)

ignore <- c("QIV2ME_5wuYC", "dhFuZR0502QC", "ULOm3_A8WrAC", "7PzlFSSx8tAC")

cites.per.year <- get_citation_history(id = "NTzu9c8AAAAJ")

cites <- get_publications(id = "NTzu9c8AAAAJ")

# This hilariously convolted bit of code just gets the h.index from the cites df
h.index <- max(which(1:nrow(cites) < cites[order(-cites$cites),"cites"]))
  
  

# Casting years to character to facilitate plotting
cites.per.year$year <- as.character(cites.per.year$year)
ggplot(cites.per.year, aes(year, cites)) + theme_bw() + geom_bar(stat="identity") + xlab("Year") + ylab("Number of Citations")
cat(paste("Total citations:   <b>", sum(as.numeric(cites.per.year$cites)), "</b>"))
cat("<br>")
cat(paste("h index:   <b>", h.index, "</b>"))
cat("<br>")
cat(paste("i-10 index:   <b>", length(which(cites$cites > 10)), "</b>"))
cat("\n\n\n")
```
</div>

```{r citations, echo = FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60), results="asis", fig.align="center"}
cites <- cites[-which(as.character(cites$pubid) %in% ignore),]
cites <- cites[order(-cites$year),]
formatted <- apply(cites, 1, function(x) paste0(x["author"], ". (", x["year"], "). ", x["title"], ". ", x["journal"], " ", x["number"], ".<br>Citations: <b>", x["cites"], "</b>"))

pandoc.list(formatted, loose = TRUE)
```